```{r results-globalSettings,include=FALSE,cache=FALSE}
read_chunk('../../R/globalSettings.r')
read_chunk('../../R/questionDistributions.r')
read_chunk('../../R/distFuncs.r')
read_chunk('../../R/loadData.r')
```
```{r globalSettings,include=FALSE}
```
```{r distFunc,include=FALSE}
```
```{r needPackages,include=FALSE}
```
```{r loadData,include=FALSE}
```

## Results \label{sec:Results}

### Entire Data
First we check the distribution of the pertinent questions when calculated on the entire data.

#### Rice
```{r riceDist,dependson=c('needPackages', 'distFunc', 'loadData')}
```
```{r results-rice-head,dependson='riceDist'}
riceAll
```
```{r ricePlot,dependson='riceDist'}
```

#### Water
```{r waterDist,dependson=c('needPackages', 'distFunc', 'loadData')}
```
```{r results-water-head,dependson='waterDist',dependson='waterDist'}
waterAll
```
```{r waterPlot}
```

#### Accomodation
```{r accommodationDist,dependson=c('needPackages', 'distFunc', 'loadData')}
```
```{r results-accommodation-head,dependson='accommodationDist'}
accommodationAll
```
```{r accommodationPlot,dependson='accommodationDist'}
```

### Sampled Data
Now we sample the data, taking samples of size 3, 4, 5, 10, 15 and 20 tehsils and build similar distributions.

```{r sampleSizes}
```

First we set the seed to ensure reproducibility.
```{r setSeedForSampling,results='hide',dependson='sampleSizes'}
```

Now we build the sampled datasets.
```{r buildSampledData,dependson='sampleSizes'}
```

And then build distributions for each of the questions for each of the sampling sizes.
#### Rice
```{r sampledRiceDist,dependson='buildSampledData'}
```

#### Water
```{r sampledWaterDist,dependson='buildSampledData'}
```

#### Accommodation
```{r sampledAccommodationDist,dependson='buildSampledData'}
```

### Compare the Results Visually
Visually we can see the results.

#### Rice
```{r plotAllRice,dependson='sampledRiceDist'}
```

#### Water
```{r plotAllWater,dependson='sampledWaterDist'}
```

#### Accommodation
```{r plotAllAccommodation,dependson='sampledAccommodationDist'}
```

### Accuracy
We computer the numerical accuracy based on Mean Squared Error (MSE).

#### Rice
```{r compareRice,dependson='plotAllRice'}
```
```{r plotMSERice,dependson='compareRice'}
```

#### Water
```{r compareWater,dependson='plotAllWater'}
```
```{r plotMSEWater,dependson='compareWater'}
```

#### Accommodation
```{r compareAccommodation,dependson='plotAllAccommodation'}
```
```{r plotMSEAccommodation,dependson='compareAccommodation'}
```

### All the MSEs together
```{r plotMSERiceWaterAccommodation}
```
