```{r results-globalSettings,include=FALSE,cache=FALSE}
read_chunk('../../R/globalSettings.r')
read_chunk('../../R/questionDistributions.r')
read_chunk('../../R/distFuncs.r')
read_chunk('../../R/loadData.r')
```
```{r globalSettings,include=FALSE}
```
```{r distFunc,include=FALSE}
```
```{r needPackages,include=FALSE}
```
```{r loadData,include=FALSE}
```

## Results

### Entire Data
First we check the distribution of the pertinent questions when calculated on the entire data.

#### Rice
```{r riceDist,dependson=c('needPackages', 'distFunc', 'loadData')}
```
```{r results-rice-head}
rice
```
```{r ricePlot}
```

#### Water
```{r waterDist,dependson=c('needPackages', 'distFunc', 'loadData')}
```
```{r results-water-head}
water
```
```{r waterPlot}
```

#### Accomodation
```{r accommodationDist,dependson=c('needPackages', 'distFunc', 'loadData')}
```
```{r results-accommodation-head}
accommodation
```
```{r accommodationPlot}
```

### Sampled Data
Now we sample the data, taking samples of size 3, 4, 5, 10, 15 and 20 tehsils and build similar distributions.

First we set the seed to ensure reproducibility.
```{r setSeedForSampling,results='hide'}
```

Now we build the sampled datasets.
```{r buildSampledData}
```

And then build distributions for each of the questions for each of the sampling sizes.
#### Rice
```{r sampledRiceDist}
```

#### Water
```{r sampledWaterDist}
```

#### Accommodation
```{r sampledAccommodationDist}
```

### Compare the Results Visually
Visually we can see the results.

#### Rice
```{r plotAllRice}
```

#### Water
```{r plotAllWater}
```

#### Accommodation
```{r plotAllAccommodation}
```

### Accuracy
